---
title: "MBO Config"
format:
  html:
    embed-resources: true
---

```{r}
#| include: false
options(datatable.print.nrows = 1000)

library(data.table)
library(ggplot2)
library(mlr3misc)
library(gt)
library(here)
library(dplyr)

archive = readRDS(here("coordinate_descent/2024_09_02_intermediate_instance.rds"))

summary = rbindlist(map(seq(nrow(archive)), function(i) {
  data.table(
    min_k = min(archive$raw_k[[i]]),
    q05 = quantile(archive$raw_k[[i]], 0.05),
    median_k = median(archive$raw_k[[i]]),
    q95 = quantile(archive$raw_k[[i]], 0.95),
    max_k = max(archive$raw_k[[i]]))
}))

archive = archive[, -c("raw_k", "raw_mean_score", "n_na", "n", "missing_instances", "x_domain", "timestamp", "iteration", "id"), with = FALSE]

archive = cbind(archive, summary)

archive[, rank := rank(-mean_k), by = batch_nr]

set(archive, i = 1L, j = "parameter", value = "start_config")

archive[, improvement := .SD[parameter == "incumbent", mean_k] < mean_k, by = batch_nr]
```

# Setup

Coordinate descent on configurations of the `mlr3mbo` package (see search space).
Each mbo configuration runs on 1286 instances from yahpogym (rbv2 and lcbench) with a budget of 200 iterations.
When the performance of the mbo run is the same as a random search with 200 iterations, the configuration scores 0.
When the performance of the mbo run is the same as a random search with 1,000,000 iterations, the score is 1.
The score is averaged over all instances.

```{r}
#| eval: false

search_space = ps(
  log_scale = p_lgl(),
  init = p_fct(c("random", "lhs", "sobol")),
  init_size_fraction = p_fct(c("0.05", "0.10", "0.25")),
  random_interleave_iter = p_fct(c("0", "2", "5", "10")),
  rf_type = p_fct(c("standard", "extratrees", "smaclike_simple", "smaclike_law_of_total_variance")),
  acqf = p_fct(c("EI", "CB", "PI", "Mean")),
  lambda = p_fct(c("1", "3", "10"), depends = acqf == "CB"),
  acqopt = p_fct(c("RS_1000", "RS", "FS", "LS")),
  epsilon_decay = p_lgl(depends = acqf == "EI"),
  lambda_decay = p_lgl(depends = acqf == "CB")
)
```



```{r}
#| echo: false
#| column: screen
#| label: tbl-mbo
#| tbl-cap: |
#|  Result of the coordinate descent.
#|  Each row is the evaluation of a configuration on 1286 instances.
#|  The green rows are the best performing configuration in each generation.
#|  The orange rows are the re-evalation of the incumbent configuration.
#|  The group rank is the rank of the configuration in the generation.
#|  The min and max score are the minimum and maximum score archived on the 1286 instances.
#|  The parameter column indicates which parameter was changed.
#|  The subheadings show the batch number and the parameter that was changed.
#|  Bold mean scores are better than the incumbent.

as_tibble(archive) %>%
 group_by(batch_nr, parameter) %>%
  gt() %>%
  tab_style(
    style = list(
      cell_fill(color = "#F9E3D6")
      ),
    locations = cells_body(
      rows = parameter == "incumbent"
    )
  ) %>%
  tab_style(
    style = list(
      cell_fill(color = "#90ee90")
      ),
    locations = cells_body(
      rows = rank == 1
    )
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
      ),
    locations = cells_body(
      columns = mean_k,
      rows = improvement == TRUE
    )
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()
  ) %>%
  fmt_number(
    columns = c("min_k", "q05", "median_k", "q95", "max_k", "mean_k"),
    decimals = 2
  ) %>%
  cols_label(
    log_scale = "Log Scale",
    init = "Init",
    init_size_fraction = "Init Size Fraction",
    random_interleave_iter = "Interleave",
    rf_type = "RF Type",
    acqf = "Acqf",
    lambda = "Lambda",
    acqopt = "Acqopt",
    epsilon_decay = "Epsilon Decay",
    lambda_decay = "Lambda Decay",
    mean_k = "Mean Score",
    batch_nr = "Batch",
    parameter = "Parameter",
    min_k = "Min Score",
    q05 = "Q.05 Score",
    median_k = "Median Score",
    q95 = "Q.95 Score",
    max_k = "Max Score",
    rank = "Group Rank"
  ) %>% tab_row_group(
    label = "numbered",
    rows = matches("^[0-9]")
  ) %>%
  cols_hide("improvement")
```

