---
title: "mlr3mbo - Configuration Mixed Dependencies"
format:
  html:
    embed-resources: true
---

```{r}
#| include: false
options(datatable.print.nrows = 1000)

library(data.table)
library(ggplot2)
library(mlr3misc)
library(dplyr)
library(gt)

here::i_am("coordinate_descent/report_pure_numeric.qmd")
archive = readRDS(here::here("coordinate_descent/results/mixed_archive.rds"))

archive[, min_meta_score := map_dbl(raw_meta_score, min)]
archive[, q05_meta_score := map_dbl(raw_meta_score, quantile, 0.05)]
archive[, median_meta_score := map_dbl(raw_meta_score, median)]
archive[, q95_meta_score := map_dbl(raw_meta_score, quantile, 0.95)]
archive[, max_meta_score := map_dbl(raw_meta_score, max)]

archive = archive[, -c("raw_meta_score", "raw_mean_score", "n_na", "n", "missing_instances", "timestamp", "iteration", "id"), with = FALSE]

archive[, rank := rank(-mean_meta_score), by = batch_nr]
set(archive, i = 1L, j = "parameter", value = "start_config")
set(archive, i = 1L, j = "batch_nr", value = 0L)

archive[, variance_estimator := map_chr(variance_estimator, function(x) {
  switch(x,
    "jack" = "Jack",
    "ensemble_standard_deviation" = "ESD",
    "law_of_total_variance" = "LTV",
    NA_character_
  )
})]

best_by_group = archive[, .(best_score = max(mean_meta_score)), by = batch_nr]
best_by_group[, best_prev := shift(best_score)]
archive = best_by_group[archive, on = "batch_nr"]
archive[, better := mean_meta_score > best_prev]
set(archive, i = 1L, j = "better", value = FALSE)
```

# Setup

Coordinate descent on configurations of the `mlr3mbo` package (see `search_space` below).
Each MBO configuration runs on the instances from YAHPO-SO v1 with a budget of 400.
When the performance of the MBO run is the same as a random search with this budget, the configuration scores 0.
When the performance of the MBO run is the same as a random search with 1,000,000 iterations, the score is 1.
The score is averaged over all `instances` (see below) and before that averaged over potential replications (currently 30).

## mlr3mbo Search Space

```{r}
#| eval: false
search_space = ps(
  input_trafo            = p_fct(c("none", "unitcube")),
  output_trafo           = p_fct(c("none", "standardize", "log")),
  init                   = p_fct(c("random", "lhs", "sobol")),
  init_size_fraction     = p_fct(c("0.05", "0.10", "0.25"), trafo = as.numeric),
  random_interleave_iter = p_fct(c("0", "2", "4"), trafo = as.integer),
  # surrogate
  trees                  = p_fct(c("10", "500"), trafo = as.integer),
  variance_estimator     = p_fct(c("jack", "ensemble_standard_deviation", "law_of_total_variance")),
  # acqf
  acqf                   = p_fct(c("EI", "CB", "PI", "Mean")),
  lambda                 = p_fct(c("1", "3", "10"), depends = acqf == "CB", trafo = as.integer),
  epsilon_decay          = p_lgl(depends = acqf == "EI"),
  lambda_decay           = p_lgl(depends = acqf == "CB"),
  # acqopt
  acqopt                 = p_fct(c("RS_1000", "RS", "LS"))
)
```

# Results

Each row is the evaluation of a configuration on the instances.
The green rows are the best performing configuration in each generation.
The group rank is the rank of the configuration in the generation.
The min and max score are the minimum and maximum score achieved on the instances.
The parameter column indicates which parameter was changed.
The subheadings show the batch number and the parameter that was changed.
Bold mean scores are better than the incumbent.

```{r}
#| echo: false
#| column: screen
#| label: tbl-mbo
#| tbl-cap: |
#|  Result of coordinate descent for mlr3mbo configuration on YAHPO-SO v1.

as_tibble(archive) %>%
 group_by(batch_nr, parameter) %>%
  gt() %>%
  tab_style(
    style = list(
      cell_fill(color = "#90ee90")
      ),
    locations = cells_body(
      rows = rank == 1
    )
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
      ),
    locations = cells_body(
      columns = mean_meta_score,
      rows = better == TRUE
    )
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()
  ) %>%
  fmt_number(
    columns = c("mean_meta_score", "min_meta_score", "q05_meta_score", "median_meta_score", "q95_meta_score", "max_meta_score", "median_meta_score"),
    decimals = 2
  ) %>%
  cols_label(
    input_trafo = "Input Trafo",
    output_trafo = "Output Trafo",
    init = "Init",
    init_size_fraction = "Init Size Fraction",
    random_interleave_iter = "Interleave",
    trees = "Trees",
    variance_estimator = "Variance Estimator",
    acqf = "Acqf",
    lambda = "Lambda",
    acqopt = "Acqopt",
    epsilon_decay = "Epsilon Decay",
    lambda_decay = "Lambda Decay",
    mean_meta_score = "Mean Score",
    batch_nr = "Batch",
    parameter = "Parameter",
    min_meta_score = "Min Score",
    q05_meta_score = "Q.05 Score",
    median_meta_score = "Median Score",
    q95_meta_score = "Q.95 Score",
    max_meta_score = "Max Score",
    rank = "Group Rank"
  ) %>% tab_row_group(
    label = "numbered",
    rows = matches("^[0-9]")
  ) %>% cols_hide(c("better", "best_prev", "best_score"))
```

